Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-09 pkg/disttree/inst/draft/rejoinder2.Rnw
- revised rejoinder and corresponding modifications in the manuscript - especially the discussion of more complex distributions should be checked again - also rejoinder on East Tyrol aspects should be improved
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2457 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d3a61fb932ac7bc551babc5d498793cb0b08415b

TO DO: adaption in the manuscript

@@

\begin{review}
I think the authors tried to address my comments and invested considerable additional work 
on simulations and predictions on more stations. I appreciate this but am still no completely 
convinced that the models can provide benefits in distributional regression problems in 
particular when the distribution is more complex. The reason is that in all models considered, 
the distribution parameters are "orthogonal" in the sense that the mean and the variance 
parameter separate well.
This is not the case for many other distributions like the Dagum, Zero-inflated models, etc. 
I am wondering how well the distributional forest in these cases works with respect to the 
splits in the different distribution parameters. For instance, the expectation of the response 
for a Dagum distribution is a function of all distribution parameters and I have doubts that 
splitting the forests works without identification issues such that the forests may get very 
sensitive with respect to the test and training data.

In addition, overall I would say the method performs as well as the competitors but loses 
interpretation and for the prespecified GAMLSS also uncertainty estimates. With uncertainty 
I mean uncertainty of the estimates no the variance of the response.

@@

Thank you very much for your feedback and the constructive comments regarding the paper. 
You are right that it still has to be tested how distributional trees and forests perform when
employing very complex distributions such as the Dagum distribution. 
However, contrary to the uncensored Gaussian distribution the parameters of the here applied 
censored Gaussian distribution are not orthogonal as changing the mean also influences the variance,
especially close-by the censoring point. Moreover, the three-parametric two-part hurdle model
employed in Supplement A is almost equivalent to the zero-inflated model you suggested. 
Hence, the distributional trees and forests have been tested for distributions with dependencies
among their parameters and have shown to perform well. But of course further investigation is
required in order to confirm these findings in general. This is now also mentioned in an additional 
subsection of the discussion in the manuscript.

>>>>

FIXME: adaption in the manuscript

FIXME: I think we should present the two arguments more side by side, i.e., mention both
early on and subsequently discuss both in more detail. (1) One factor is that only a single
split into 28 years of training and 4 years of test data is considered in the main manuscript.
When doing the full cross-validation the pronounced differences between the methods are much
diminished. (2) East Tyrol is in a different climate zone and hence effects could be more
additive and with less interactions than in North Tyrol.

@@

\begin{review}
I think the authors tried to address my comments and invested considerable additional work 
on simulations and predictions on more stations. I appreciate this but am still no completely 
convinced that the models can provide benefits in distributional regression problems in 
particular when the distribution is more complex. The reason is that in all models considered, 
the distribution parameters are ``orthogonal'' in the sense that the mean and the variance 
parameter separate well.
\end{review}

Thank you for emphasizing this issue. We have now included some explicit pointers in Section~4
to the previous random forest literature where it is indeed shown that the advantages of score-based
split selection are particularly pronounced when the parameters are orthogonal. In contrast,
when parameters are closely correlated with the distribution mean then the advantages are
diminished and different random forest flavors typically perform similarly.

Our results confirm these findings in the context of parametric distributional modeling,
showing that results are quite robust to the distributional specification. Note also that
in our models mean and variance are typically quite closely correlated due to the substantial
censoring at zero (or truncation/zero-inflation in Supplement~A).

\begin{review}
This is not the case for many other distributions like the Dagum, Zero-inflated models, etc. 
I am wondering how well the distributional forest in these cases works with respect to the 
splits in the different distribution parameters. For instance, the expectation of the response 
for a Dagum distribution is a function of all distribution parameters and I have doubts that 
splitting the forests works without identification issues such that the forests may get very 
sensitive with respect to the test and training data.
\end{review}

We do not expect identification issues but agree that the advantages over a method like
Meinshausen's quantile regression forests will likely decrease or even disappear. However,
we do not speculate about these properties in the manuscript but do point out that this
deserves exploration in future research.

\begin{review}
In addition, overall I would say the method performs as well as the competitors but loses 
interpretation and for the prespecified GAMLSS also uncertainty estimates. With uncertainty 
I mean uncertainty of the estimates no the variance of the response.

@@

FIXME: Torsten, should we comment on this? In a predictive setup like the precipitation
forecasting the uncertainty of the estimates is not of so much concern. Also, the 
uncertainty due to variation in the response is typically much larger.
